### 2025-04-22 paper/ecai2025/sects/related.tex
update to ecai 2025 template

\paragraph{Reinforcement Learning on Differentiable Engines}
Precursors of SHAC with similar intuition are PODS~\cite{Mora21} and CE-APG~\cite{Gillen22}. In~\cite{Lv23}, the authors introduce rendering to enhance model-based RL. \cite{Zheng24} employes a differentiable symbolic expression search engine. Trajectory optimization approach is taken in~\cite{Wan24}. \cite{Georgiev24} takles unstable gradient due to stiff dynamics by adaptively truncating trajectories when these occur. With respect to this approach, we take a substantially different method, by emulating the differentiable environment with a trained neural network.

>>>>

\paragraph{Reinforcement Learning on Differentiable Engines}
Precursors of SHAC with similar intuition are PODS~\cite{Mora21} and CE-APG~\cite{Gillen22}. In~\cite{Lv23}, the authors introduce rendering to enhance model-based RL\@.\ \citet{Zheng24} employ a differentiable symbolic expression search engine. Trajectory optimization approach is taken in~\cite{Wan24}.\ \citet{Georgiev24} tackles unstable gradient due to stiff dynamics by adaptively truncating trajectories when these occur. With respect to this approach, we take a substantially different method, by emulating the differentiable environment with a trained neural network.
